---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cangetpop


The goal of cangetpop is to return the canadian population within a polygon.
There are helper functions to generate a circle of any given radius (in kilometers) around a given longitude.  



## Installation

You can install cangetpop from github using

``` r
devtools::install_github("simoncoulombe/cangetpop")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
suppressMessages(
  suppressWarnings({
    library(dplyr)
    library(magrittr)
    library(cangetpop)
    library(osmdata)
    library(sf)
    library(purrr)
    library(cancensus)
    library(mapview)
  })
)
## basic example code
```


get_populations_from_address_radius() needs an address (without the postal code) and a radius in kilometers:

```{r}
data1 <- get_populations_from_address_radius("CN tower, toronto, canada", 1 )
print(data1)
```


```{r, fig.width=12}
mapview(data1)
```

get_populations_from_lat_lon_radius() needs a latitude and longitude (in degrees)  and a radius in kilometers:

```{r}
data2 <- get_populations_from_lat_lon_radius(45, -65, 1 )
data2
```

```{r, fig.width=12}
mapview::mapview(data2)
```


get_populations_from_polygon() simply takes a polygon as input

```{r}
bb_sf <- getbb("Quebec, QC", format_out = "sf_polygon")[1,] ## polygon of quebec city
data3 <- get_populations_from_polygon((bb_sf))
data3
```

```{r, fig.width=12}
mapview(data3, zcol ="Population")
```


Here's an example returning the population around the 14 "Ashton" restaurants in Quebec city

Voici les coordonnées des restaurants Ashton de Québec trouvées avec {osmdata}

```{r}
bb <- getbb("Quebec, QC")

x <- bb %>% opq() %>%
  add_osm_feature(key= "name", value = c("ASHTON", "ASTHON"),
                  value_exact = FALSE, match_case = FALSE
  )%>%
  osmdata_sf()

ashton <- x$osm_points %>% 
  filter(!(osm_id %in% c(1750439777,1750439789, 1750439808, 1750439833,  1750439845, 1616297363, 1616297367, 1616297399)))  %>% ## some restaurants have multiple points.. keep only one
  dplyr::mutate(longitude = sf::st_coordinates(.)[,1],
                latitude = sf::st_coordinates(.)[,2])



data0 <- ashton %>% 
  st_drop_geometry() %>% 
  select(osm_id, latitude, longitude) %>% 
  mutate( pouet = pmap(list(latitude, longitude, 1),
                       get_populations_from_lat_lon_radius)
  )

final_ashton_data <- bind_rows(data0$pouet) %>% bind_cols(data0 %>% select(-pouet)) %>% mutate(Population = round(Population))

final_ashton_data

```

```{r, fig.width=12}
mapview(final_ashton_data, zcol = "Population")
```

